Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-08 manuscript.tex
Appendix updates

In this Appendix we present the same analysis as presented in Sec.~\ref{sec:4} for those four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).

Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and some of the results based on the Normal fit. The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B. The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV for all the considered stars. The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.  Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq. \ref{eq:RV:correction}. Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on $\text{HD}215152$ and Corot-7, whose measurements have lower SNR with respect to the previous two analyzed stars, suggest that the residuals for the Normal are 0.05 and 0.34\,\ms\,higher than the residuals retrieved with the SN analysis, respectively.

>>>>

In this Appendix, a similar analysis as presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V). \jessi{Are there papers that can/should be cited here for the datasets used?}

Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal models. 
These results are consistent with those from the analysis of Alpha Centauri B. 
The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and Normal mean RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV \jessi{was the RV for these other asymmetry papers the Normal mean RV?} for all the considered stars. 
The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV \jessi{N mean RV?} for three of the four stars.  Also for all these stars the originally estimated RVs were corrected from spurious variations in RVs caused by stellar activity using Eq. \ref{eq:RV:correction}. 
Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. 
The stellar activity-corrected Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.  $\text{HD}215152$ and Corot-7 have  lower SNR than the other two analyzed stars.  \jessi{was the SNR of the four stars stated anywhere?  If not, if we want to keep the last point, we should note what the SNR of the stars are.}
